### 2012-02-09 GUIErrorDetector/paper/evaluation.tex
many tweaks

\section{Empirical Evaluation}
\label{sec:evaluation}

@@

\begin{itemize}
\Item \textbf{SWT desktop applications.}
%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
file backup solution for Linux and Windows.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.15\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
\cline{2-11}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
\hline \hline
\multicolumn{11}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
 \hline
 ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
 \hline
 \hline
\multicolumn{11}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
 \hline
 \hline
\multicolumn{11}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
 \hline
 \hline
\multicolumn{11}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
\hline
\hline
 Total & 199161 / 199724 &  188 / 251 & 6 / 6 & 149441 / 153054& 137 / 137& 7 / 7 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA '', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using normal call graph construction algorithm and the reflection-aware
call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of a straightforward approach, called ``Requiring Wrappers'' (Section~\ref{sec:straightforward}),
are shown at the far right.} }
\end{table*}

\subsection{Results}
\label{sec:results}

%Table~\ref{table:results} show the errors in
%our subject programs, and Table~\ref{table:filters} show
%the effect of applying each heuristic filter.

@@

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with fewer false positive warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introducing imprecision. Although the error-revealing path exists in
the less precise graphs, it presents the error detection algorithm finding it.
Figure~\ref{fig:ex} illustrates this limitation.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.33]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
\CodeIn{safeMtd} is a Safe UI method, and \CodeIn{uiAcc} is a UI-Accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. The node for \CodeIn{Thread.run()}
method is omitted for brevity. Using the less precise call graph, the error
detection algorithm will report an invalid method call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()},
but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{uiAcc()}. The
actual error path can only be found when using the more precise call graph.
}}
\end{figure}

@@

\noindent \textbf{\textit{Summary.}} Although a static analysis may
issue false positives or redundant reports, a set of well-designed
sound and heuristic filters can still remove most of them.
%Heuristic filter, effective.

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.46\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 & \multicolumn{6}{|c|}{Number of Warnings}  \\
\cline{2-7}
 Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
\cline{3-7}
 Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
 \hline
 FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
 \hline
 ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1644 &  1644 &  1644 & 1644 &  6 & 6\\
 \hline
 HundsonEclipse&  1367 &  567 &  567 & 567 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  31978 & 30975 &  9 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 58  &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
 \hline
 MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
\hline
 \hline
 Total &  60631 &  40461 &  39764 &  37421 &  112 & 22 \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
sound and heuristic filters. Column ``Before Filtering''
shows the number of warnings by the reflection-aware 1-CFA algorithm.
Other algorithms show similar patterns, which are omitted for brevity.
Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
The numbers in the last column are the same as the subcolumn ``\#Warning"
under column ``1-CFA'' in Table~\ref{table:results}.
} }
\end{table}

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in two aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.

>>>>

\tinystep
\section{Empirical Evaluation}
\label{sec:evaluation}

@@

\begin{itemize}%\addtolength{\itemsep}{-0.5\baselineskip}
\Item \textbf{SWT desktop applications.}
%VirgoFTP~\cite{virgo} and FileBunker~\cite{filebunker} are two useful SWT desktop applications.
VirgoFTP~\cite{virgo} implements a simple FTP client based on Java and SWT UI library.
FileBunker~\cite{filebunker} is a file backup application which uses one or more GMail
accounts as its backup repository. ArecaBackup~\cite{areca} offers a local
file backup solution for Linux and Windows.

@@

\begin{table*}[ht]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\hspace*{-0.2cm}
\setlength{\tabcolsep}{.15\tabcolsep}
\begin{tabular}{|l||c|c|c||c|c|c||c|c|c||c|}
\hline
 Subject&  \multicolumn{9}{|c||}{Our Technique} & Requiring Wrappers  \\
\cline{2-10}
 Program  &  \multicolumn{3}{|c||}{RTA }& \multicolumn{3}{|c||}{0-CFA } & \multicolumn{3}{|c||}{1-CFA } & (Section~\ref{sec:straightforward})  \\
\cline{2-11}
 & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & CG Size & \#Warning & \#Bug & \#Warning \\
\hline \hline
\multicolumn{11}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP&  12401 &  1 &  1 & 10858 & 1 & 1 & 43598 & 2 & 2& 149  \\
 \hline
 FileBunker &  18951 &  1 &  0 & 15743 & 0 & 0 & 76088 & 2 & 1& 693  \\
 \hline
 ArecaBackup&  20882 &  1  &  0 & 19697 & 1 & 1  & 116398 & 1 & 1 & 3021\\
 \hline
 \hline
\multicolumn{11}{|l|}{Eclipse plugins}   \\
 \hline
 EclipseRunner&  11248&  6 &  1 & 7201 & 6 & 1 & 26911 & 6 & 1& 202  \\
 %\hline
 %FileSync&  12132 &  xx &  xxx &8235 & xx & xx& 32565 & 1 & 1 & 331 & 1 \\
 \hline
 HudsonEclipse& 18473 &  2 &  1 & 15814 & 2 & 1& 56645 & 3 & 1 & 182 \\
 \hline
 \hline
\multicolumn{11}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox & 37751 &  0 &  0 & 30609 & 0 & 0 & 115324 & 1 & 1 & 210  \\
 \hline
  SudokuSolver&  27730&  3 &  2 & 20907 & 3 & 2 & 39299 & 2 & 2 & 356  \\
 \hline
 \hline
\multicolumn{11}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler & 13631 / 13865&  12 / 16 &  0 / 0 & 9546 / 9682& 4 / 4& 1 / 1 & 35198 / 35756 & 1 / 1  & 1 / 1& 104 \\
 \hline
 Fennec & 14058 / 14387 &  1 / 1 &  0 / 0 & 8263 / 8898 & 1 / 1 & 0 / 0& 29125/ 31759 & 3 / 3 & 1 / 1& 433 \\
 \hline
 MyTracks & 24036 / 24036 &  161 / 220 & 0 / 0 & 10803 / 13645 & 119 / 119 & 0 / 0 & 39235 / 110977 & 1 / 1 & 0 / 1 & 1192 \\
\hline
\hline
 Total & 199161 / 199724 &  188 / 251 & 5 / 5 & 149441 / 153054& 137 / 137& 6 / 6 & 577821 / 652756& 22 / 22 & 11 / 12 & 6542\\
\hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:results}Experimental results in finding invalid thread access errors
in multithreaded GUI programs. Column ``CG Size'' shows the
call graph size in terms of node number. Column ``\#Warning''
shows the number of warnings issued by our tool. Column ``\#Bug'' shows
the actual bugs found. Columns ``RTA '', ``0-CFA'',
and ``1-CFA'' show the results of using different
call graph construction algorithms. In each cell of the table
for Android applications, a slash ``/'' separates the result of
using standard call graph construction algorithm and the reflection-aware
call graph construction algorithm. The \newbugs errors found in VirgoFTP, FileBunker, ArecaBackup
S3dropbox, and SudokuSolver are previously  unknown. As a comparison, the
results of the ``Requiring Wrappers'' approach (Section~\ref{sec:straightforward}),
are shown at the far right.} }
\end{table*}

\tinystep
\subsection{Results}
\label{sec:results}

%Table~\ref{table:results} show the errors in
%our subject programs, and Table~\ref{table:filters} show
%the effect of applying each heuristic filter.
\smallstep

@@

We next compare the three call graph construction algorithms (RTA, 0-CFA, and 1-CFA)
used in our experiments. As shown in Table~\ref{table:results},  1-CFA found
more errors with fewer false positive warnings than the other two algorithms. This
is because RTA and 0-CFA do not consider the calling context when
constructing a call graph, and may
mix the same method calls by different callers into a single node, thus
introducing imprecision. Although the error-revealing paths exist in
less precise graphs, the impreicison prevents our algorithm finding them.
Figure~\ref{fig:ex} illustrates this point.

\begin{figure}[t]
  \centering
  \includegraphics[scale=0.45]{cgexample}
  \vspace*{-5.0ex}\caption {{\label{fig:ex} (a) shows an example code, in which
\CodeIn{safe()} is a Safe UI method, and \CodeIn{uiAcc()} is a UI-Accessing method.
(b) shows a less precise call graph built by RTA or 0-CFA, and (c) shows a more
precise call graph built by 1-CFA. Nodes for constructors are omitted for brevity.
Using the less precise call graph, the error
detection algorithm in Figure~\ref{fig:detectalgorithm} will report an invalid method call chain: \CodeIn{entry()}
$\rightarrow$ \CodeIn{f()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()}
$\rightarrow$ \CodeIn{uiAcc()},
but miss the actual error path: \CodeIn{entry()} $\rightarrow$ \CodeIn{g1()} $\rightarrow$
\CodeIn{g2()} $\rightarrow$ \CodeIn{start()} $\rightarrow$ \CodeIn{run()} $\rightarrow$ \CodeIn{uiAcc()}. The
actual error path can only be found when using the more precise call graph.
}}
\end{figure}

@@

\noindent \textbf{\textit{Summary.}} Although a static analysis may
issue false positives or redundant reports, a set of well-designed
error filters can remove most of them.
%Heuristic filter, effective.

\begin{table}[t]
\begin{center}
 \fontsize{9pt}{\baselineskip}\selectfont
\setlength{\tabcolsep}{.46\tabcolsep}
\hspace*{-0.2cm}
\begin{tabular}{|l||c|c|c|c|c|c|}
\hline
 & \multicolumn{6}{|c|}{Number of Warnings}  \\
\cline{2-7}
 Subject & Before & \multicolumn{2}{|c|}{Sound Filters}  &  \multicolumn{3}{|c|}{Heuristic Filters}  \\
\cline{3-7}
 Program &Filtering  & $F_1$ & $F_{1,2}$ & $F_{1,2,3}$&$F_{1,2,3,4}$ & $F_{1,2,3,4,5}$\\
\hline \hline
\multicolumn{7}{|l|}{SWT desktop applications}   \\
 \hline
 VirgoFTP &  21 &  21 &  21 & 7 &  2 & 2\\
 \hline
 FileBunker &  4494 &  4494 &  4494 &  3210 &  10  & 2\\
 \hline
 ArecaBackup &  6219 &  438 & 438 &  438  &  1 & 1\\
 \hline
 \hline
\multicolumn{7}{|l|}{Eclipse plugins}   \\
 %\hline
 %EclipseRunner &  xxxx &  xx &  xxx & xx &  xxx & xx\\
 \hline
 EclipseRunner&  1644 &  1644 &  1644 & 1644 &  6 & 6\\
 \hline
 HundsonEclipse&  1367 &  567 &  567 & 567 &  3 & 3\\
 \hline
 \hline
\multicolumn{7}{|l|}{Swing desktop applications}   \\
 \hline
 S3dropbox&  45528 &  31978 &  31978 & 30975 &  9 & 1\\
 \hline
 SudokuSolver &  58 &  58 &  58 & 58  &  2 & 2\\
 \hline
 \hline
\multicolumn{7}{|l|}{Android mobile applications}   \\
 \hline
 SGTPuzzler&  2 &  1 &  1 & 1 &  1 & 1\\
 \hline
 Fennec &  122 &  84 & 80 & 80 &  9 & 3\\
 \hline
 MyTracks &  1176 &  1176 &  483 & 441 &  69 & 1 \\
\hline
 \hline
 Total &  60631 &  40461 &  39764 &  37421 &  112 & 22 \\
 \hline
\end{tabular}
\end{center}
\vspace{-15pt}
\Caption{{\label{table:filters}Number of warnings after applying a set of
sound and heuristic error filters. Column ``Before Filtering''
shows the number of warnings by the reflection-aware 1-CFA algorithm.
Other algorithms show similar patterns, which are omitted for brevity.
Column ``$F_{i,...,j}$'' represents the number of remaining warnings after applying
the $i$th to $j$th filters as defined in Section~\ref{sec:heuristic}.
The numbers in the last column are the same as the subcolumn ``\#Warning"
under column ``1-CFA'' in Table~\ref{table:results}.
} }
\end{table}

@@

\noindent \textbf{\textit{Limitations.}}
Our technique is limited in three aspects. First, it only considers
non-UI threads that are spawned by the UI-thread after the GUI
is initialized, and ignores other possible non-UI threads (quite unusual)
that are created during the pre-initialization GUI work. One way
to remedy this limitation is to design an analysis to identify
those non-UI threads created before a GUI is launched.
Second, like many bug-finding techniques, our technique
is neither sound nor complete. It may miss true positives due
to the graph search strategy the algorithm employs, or
issue false positives because the conservative nature of
a static analysis. Designing better call graph construction
and search algorithm may alleviate this limitation.
Third, our tool cannot compute call relationships
for inter-process communication between components. It also
requires users to manually add annotations to characterize
call relationships that involve native methods. This limitation
may lead to false negatives. Investigating the false negative
rate is ongoing work.

### 2012-02-09 GUIErrorDetector/paper/technique.tex
many tweaks

Given a sound call graph, our algorithm is sound in that it does not
miss true positives. We note, however, that computing a sound
call graph in the presence of reflection and native methods is non-trivial. 
To alleviate this problem, we next proposed a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg} and annotation support
for native methods in Section~\ref{sec:annotation}.

@@

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a call graph $\mathit{cg}$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\FOR{each $\mathit{statement}$ in $\mathit{P}$}
\IF{isReflectionCall($statement$)}
\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{statement}$)
\STATE $\mathit{newStmt}$ $\leftarrow$ createObjectCreationStatement($\mathit{objectSet}$)
\STATE replace $\mathit{statement}$ with $\mathit{newStmt}$
\ENDIF
\ENDFOR
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\RETURN $\mathit{cg}$
%\ENDWHILE
\end{algorithmic}
\vspace{-3mm}
\caption{A reflection-aware call graph construction algorithm. Lines
1--7 are a simple program transformation to replace reflection calls
with object creations, and line 8 builds the call graph using
an existing call graph construction algorithm. This algorithm
is parameterized by two methods on lines 2 and 3. 
How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
%This algorithm is parameterized by the call graph construction
%algorithm on line 8, in which any existing algorithm can be used.
} 
\label{fig:cgalgorithm}
\end{figure}

%GUI applications tend to use reflection intensively. In particular,
GUI applications built on top of the Android framework
use configuration files and reflection to specify GUI layout.
As a result, call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9--11) updates the text.
%d caches
%the current view to a list declared at line 2.

When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
fail to conclude that the variable \CodeIn{button} declared at line 6
points to a \textit{non-null} \CodeIn{Button} object due to its limitation in deal with the
reflection call \CodeIn{findViewById}, and exclude the calling edge
corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.

%. As a result, the built 
%call graph will exclude the calling edge corresponding to the
%\CodeIn{setText} method call on line 10.

%Existing call graph algorithms failed either suffer from the problem of incompleteness
%or imprecision. The k-CFA algorithm performs points-to analysis with call
%graph construction interleavingly, and maintains a value set for every expression.
%For example, it concludes that variable \CodeIn{cachedViews} can only point
%to a \CodeIn{LinkedList} object and the method call \CodeIn{add} at line 12
%can only correspond to \CodeIn{LinkedList.add}. However, k-CFA fails to
%conclude that variable \CodeIn{button} declared at line 7 points to
%a \CodeIn{Button} object due to its limitation in dealing with reflection. Thus, k-CFA
%may miss the call graph edge corresponding to the method call \CodeIn{setText} at line 11. 
%On the other hand, using a coarse-grained algorithm like RTA~\cite{} can not still
%fully solve this problem. RTA adds an edge for a method invocation 
%to the call graph if an object of the receiver's type (or subtype)
%has been created.  By explicitly specifying that all GUI classes declared in the XML file will be created,
%RTA maintains a global value set for those GUI object type, and  adds a
%call edge \CodeIn{setText} to the call graph. However, RTA introduces 
%unnecessary precision loss: it may
%may conclude that the \CodeIn{cachedViews} variable at line 2
%point to any created \CodeIn{List} objects created somewhere else in the program, despite the
%fact that \CodeIn{cachedViews} can only be a \CodeIn{LinkedList} object.

To address this limitation, we present an algorithm to construct
a reflection-aware call graph based on a simple program transformation.
The basic idea is to replace reflection calls with explicit object
creation statements, pretending that the corresponding concrete object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step (lines 1 -- 7) is a simple program
transformation to replace reflection calls with object creation statements, and
the second step (line 8) uses an existing call graph construction algorithm
to build the graph on the transformed program. In our context,
a reflection call represents a framework-specific helper method invocation
that uses Java reflection to create desirable objects, such as
the \CodeIn{findViewById} method in Android applications, instead
of the methods in the \CodeIn{java.lang.reflection} package.
%In Figure~\ref{fig:cgalgorithm}, lines 1--7 show
%the first step of program transformation. The algorithm iterates through every statement
%in an analyzed program.
When it sees a reflection call, the algorithm
determines a set of possible objects that might be created.
After that, the algorithm creates a statement that non-deterministically
returns a new object from the object set.
%Line 8 is the second step
%to build a call graph on the transformed program.

This algorithm is parameterized by two methods on
lines 2 and 3. When instantiated for the Android framework,
the predicate isReflectionCall on line 2 returns true
if the $statement$ is a \CodeIn{findViewById(id)} method call, and the method
getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
file in an Android application to extract the class declaration
 corresponding to the given \CodeIn{id} value. If the \CodeIn{id}
value is dynamically generated, this method will conservatively
return instances of all subclasses of the declared type.
%On line 8, any existing call graph construction algorithm can be applied.

Take the code in Figure~\ref{fig:sampleandroid} as an example.
When the algorithm sees the reflection call
\CodeIn{findViewById(R.id.button\_id)}, it
parses the XML configuration file to determine that the \CodeIn{button\_id}
value is mapped to a \CodeIn{Button} instance. Then, it
replaces the reflection call
with an explicit object creation statement: \CodeIn{new Button(null)}.
After that, the algorithm employs existing call graph construction
algorithms to analyze the transformed program, and permits them
to add the call edge \CodeIn{setText} to the resulting graph.

@@

%\item
\textbf{2. Filter Reports With User-Annotated Methods}. Besides general
library calls, users are also permitted to explicitly annotate project-specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed. In our experiments, we produced a list of \filternum
annotated methods for two subjects because they are using a customized
pattern to interact with the GUI framework.

%during analyzing programs on different GUI frameworks; we did this
%only between experiments rather than biasing experiments by tuning
%our tool to specific programs.

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
We encoded a list of 25 common library calls by proposing
a basic set of library calls that seemed natural and
generally applicable, based on our programming experience.
We later added other calls we found helpful in analyzing
programs and that we believed would be generally useful.

>>>>

%Given a sound call graph, our algorithm is sound in that it does not
%miss true positives. We note, however, 
For some modern GUI applications, computing a good
call graph in the presence of reflection and native methods is non-trivial. 
To alleviate this problem, we next present a reflection-aware call graph
construction algorithm in Section~\ref{sec:cg} and annotation support
for native methods in Section~\ref{sec:annotation}.

@@

\begin{figure}[t]
\textbf{Input}: a Java program $\mathit{P}$\\
\textbf{Output}: a call graph $\mathit{cg}$\\
\vspace{-5mm}
\begin{algorithmic}[1]
\FOR{each $\mathit{statement}$ in $\mathit{P}$}
\IF{isReflectionCall($statement$)}
\STATE $\mathit{objectSet}$ $\leftarrow$ getAllObjectsThatMaybeCreated($\mathit{statement}$)
\STATE $\mathit{newStmt}$ $\leftarrow$ createObjectCreationStatement($\mathit{objectSet}$)
\STATE replace $\mathit{statement}$ with $\mathit{newStmt}$
\ENDIF
\ENDFOR
\STATE $\mathit{cg}$ $\leftarrow$ constructCallGraph($\mathit{P}$)
\RETURN $\mathit{cg}$
%\ENDWHILE
\end{algorithmic}
\vspace{-3mm}
\caption{A reflection-aware call graph construction algorithm. Lines
1--7 are a simple program transformation to replace reflection calls
with object creations, and line 8 builds the call graph using
an existing call graph construction algorithm. This algorithm
is parameterized by two methods on lines 2 and 3. 
How to instantiate it for the Android framework is presented in Section~\ref{sec:cg}.
} 
\label{fig:cgalgorithm}
\end{figure}

%GUI applications tend to use reflection intensively. In particular,
GUI applications built on top of the Android framework
use configuration files and reflection to specify GUI layout.
As a result, call graph construction algorithms such as RTA~\cite{rta}
and k-CFA~\cite{kcfa} fail to build a sufficiently complete call graph.
The example code in Figure~\ref{fig:sampleandroid} from an Android application
 illustrates the limitations.
In Figure~\ref{fig:sampleandroid}, line 6 uses reflection to create a \CodeIn{Button}
object by looking up its id declared in the associated XML file. When this button
is clicked, its event handling code (lines 9--11) updates the text.

When analyzing the code in Figure~\ref{fig:sampleandroid}, existing call graph algorithms
fail to conclude that the variable \CodeIn{button} declared on line 6
points to a \textit{non-null} \CodeIn{Button} object due to its limitation in handling the
reflection call \CodeIn{findViewById}, and exclude the edge
corresponding to the \CodeIn{setText} method call on line 10 in the resulting call graph.

To address this limitation, we present an algorithm to construct
a reflection-aware call graph based on a simple program transformation.
The basic idea is to replace reflection calls with explicit object
creation statements, pretending that the corresponding concrete object
has been created.  The algorithm is shown in Figure~\ref{fig:cgalgorithm}.
It consists of two steps. The first step (lines 1 -- 7) is a simple program
transformation to replace reflection calls with object creation statements, and
the second step (line 8) uses an existing call graph construction algorithm
to build the graph on the transformed program. In our context,
a reflection call represents a framework-specific helper method invocation
that uses Java reflection to create desirable objects, such as
the \CodeIn{findViewById} method in Android applications, instead
of the methods in the \CodeIn{java.lang.reflection} package.
When it sees a reflection call, the algorithm
determines a set of possible objects that might be created.
After that, the algorithm creates a statement that non-deterministically
returns a new object from the object set.

This algorithm is parameterized by two methods on
lines 2 and 3. When instantiated for the Android framework,
the predicate isReflectionCall on line 2 returns true
if the $statement$ is a \CodeIn{findViewById(id)} method call, and the method
getAllObjectsThatMaybeCreated on line 3 parses the associated XML configuration
file to extract the class declaration
 corresponding to the given \CodeIn{id} value. If the \CodeIn{id}
value is dynamically generated, this method will conservatively
return instances of all subclasses of the declared type.
%On line 8, any existing call graph construction algorithm can be applied.

Take the code in Figure~\ref{fig:sampleandroid} as an example.
When the algorithm sees the reflection call
\CodeIn{findViewById(R.id.button\_id)}, it
parses the XML configuration file to determine that the \CodeIn{button\_id}
value is mapped to a \CodeIn{Button} instance. Then, it
replaces the reflection call
with an explicit object creation statement: \CodeIn{new Button(null)}.
After that, the algorithm employs existing call graph construction
algorithms to analyze the transformed program, and permits them
to include the call edge \CodeIn{setText} in the resulting graph.

@@

%\item
\textbf{2. Filter Reports With User-Annotated Methods}. Users are
permitted to explicitly annotate project-specific methods
that will never trigger an error.
%For example, the Android GUI framework provides a utility method 
%\CodeIn{runOnUIThread} to check whether the current thread is the UI thread
%before executing the code. If the current thread is not the UI thread,
%this method will be executed on the UI thread via message passing.
%Thus,
A reported method call chain containing an annotated  method
can be safely removed. In our experiments, we produced a list of \filternum
annotated methods for two subjects because they are using a customized
pattern to interact with the GUI framework.

@@

\textbf{3. Filter Reports Containing Library Calls}. A
method call chain containing certain library calls
like \CodeIn{Runtime.}\CodeIn{shutDown} are unlikely to
be buggy. For example, the \CodeIn{Runtime.}\CodeIn{shutDown}
method is called when JVM terminates, and uses multithreading
to dispose all GUI objects when the program exits.
We encoded a list of 25 common library calls by proposing
a basic set of library calls that seemed %natural and
generally applicable, based on our programming experience.
We later added other calls we found helpful in analyzing
programs on different GUI frameworks and that we believed would be generally useful.
We did this only between experiments rather than biasing experiments by tuning
our tool to specific programs.
